A higher order approximate static condensation method for multi-material diffusion problems

### 2018-11-26 asc.tex
added co-authors and diffusion to the title

\title{A higher order approximate static condensation method for multi-material problems}
\author{
Alexander Zhiliakov\thanks{Department of Mathematics, University of Houston, Houston, Texas 77204 (alex@math.uh.edu).}
\and Daniil Svyatskiy\thanks{Los Alamos National Laboratory, Los Alamos,
New Mexico, USA (dasvyat@lanl.gov).}
\and
Maxim Olshanskii\thanks{Department of Mathematics, University of Houston, Houston, Texas 77204 (molshan@math.uh.edu); Partially supported by NSF through grant  DMS-1717516.}
}

>>>>

\title{A higher order approximate static condensation method for multi-material diffusion problems}
\author{
Alexander Zhiliakov\thanks{Department of Mathematics, University of Houston, Houston, Texas 77204 (alex@math.uh.edu).}
\and Daniil Svyatskiy\thanks{Los Alamos National Laboratory, Los Alamos,
New Mexico, USA (dasvyat@lanl.gov).}
\and
Maxim Olshanskii\thanks{Department of Mathematics, University of Houston, Houston, Texas 77204 (molshan@math.uh.edu); Partially supported by NSF through grant  DMS-1717516.}
\and Evgeny Kikinzon \thanks{Los Alamos National Laboratory, Los Alamos,
  New Mexico, USA (kikinzon@lanl.gov).}
\and Mikhail Shashkov\thanks{Los Alamos National Laboratory, Los Alamos,
  New Mexico, USA (shashkov@lanl.gov).}
}
